Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Let's not say this

\theoremstyle{definition}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

@@

@@

        \path (p) edge (a) edge (c)
            (a) edge (d)
            (c) edge (d);
    \end{tikzpicture}
    \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
    \label{fig:klessexample}
\end{figure}

@@

For $k = 0$, we see many points above the $x-y$ diagonal, which shows that for many instances, we
are able to create a substantial number of new constraints at the top of search; on the other hand,
there are also points on the diagonal, which shows that sometimes this technique provides no
benefit. (Occasionally, points fall below the $x-y$ diagonal.  This is because the use of
neighbourhood degree sequence reasoning on supplemental graphs can also lead to increased domain
filtering, which could in turn eliminate a higher proportion of forbidden than permitted assignment
pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal diminishes, but we are
still able to create new constraints for many instances. By the time $k = 3$, most of the benefit is
disappearing---although sometimes we are still able to make a difference, and bear in mind that
sometimes adding just one new constrained pair can vastly reduce the search space.  A closer
inspection of the raw data shows that for $k \ge 3$, nearly all of the instances showing a strong
improvement are from the ``LV'' family of graphs.

>>>>

\theoremstyle{definition}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{example}{Example}

@@

\begin{example}
Take a pattern graph $P$ with vertices $V=\{p, a, b, c, d\}$ and edges $E=\{(a,d), (a,p), (b,c),
(b,d), (b,p), (c,d), (c,p)\}$, which is shown in \cref{fig:klessexample} along with two target
graphs $T_{1}$ and $T_{2}$. The degree of the vertex $p$ in $P$ is $\deg(p)=3$, the neighbours of
$p$ are $\N(p)=\{a,b,c\}$, the neighbourhood degree sequence of $p$ is $\nds(p)=(3,3,2)$, as the
degrees of the neighbours of $p$ are $\deg(a)=2,\ \deg(b)=3$ and $deg(c)=3$.

We can find a subgraph in $T_{1}$ which is non-induced isomorphic to $P$ (indicated through the bold edges and black vertices in $T_{1}$). The vertex $p$ can be  mapped to $t_{1}$ in the target graph $T_{1}$, where $\deg(t_{1})=5$ and $\nds(t_{1})=(5,5,4,2,2)$.

There is a non-induced mapping of the pattern graph $P$ into $T_{2}$ by removing one vertex of $P$. This removal changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$, to $\nds(p)=(2,2)$.

@@

        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$t_{1}$};

@@

        \path (p) edge (a) edge (c)
            (a) edge (d)
            (c) edge (d);
    \end{tikzpicture}
    \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
    \label{fig:klessexample}
\end{figure}
\end{example}

@@

For $k = 0$, we see many points above the $x-y$ diagonal, which shows that for many instances, we
are able to create a substantial number of new constraints at the top of search; on the other hand,
there are also points on the diagonal, which shows that sometimes this technique provides no
benefit. (Occasionally, points fall below the $x-y$ diagonal.  This is because the use of
neighbourhood degree sequence reasoning on supplemental graphs can also lead to increased domain
filtering, which could in turn eliminate a higher proportion of forbidden than permitted assignment
pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal diminishes, but we are
still able to create new constraints for many instances. By the time $k = 3$, most of the benefit is
disappearing---although sometimes we are still able to make a difference, and bear in mind that
sometimes adding just one new constrained pair can vastly reduce the search space.
